Clean data

### 2019-06-21 analysis/01_check-design.Rmd
Create data subfolders, update import/export code

# Load design
design <- read_csv(here("data", "design.csv"))

@@

# Save dummy-coded design output
write.csv(dummy_design, here("data", "dummy_design.csv"))
```

>>>>

# Load design
design <- read_csv(here("data", "derived_data", "design.csv"))

@@

# Save dummy-coded design output
write.csv(dummy_design, here("data", "derived_data", "dummy_design.csv"))
```

### 2019-06-21 analysis/02_clean-data.Rmd
Removed duplicate design information from final data
Create data subfolders, update import/export code

col_names <- names(read_csv(here::here("data", "conjointqsf_final.csv")))
data <- read_csv(
  here::here("data", "conjointqsf_final.csv"),
  skip = 2,
  col_names = col_names
)
```

@@

```{r clean-data, warning=FALSE, message=FALSE}
design_orig <- read_csv(here("data", "design.csv")) %>% 
  rename(
    version = question_set,
    task = question,
    alt = choice
  ) %>% 
  gather(key = "atts", value = "levels", -c(version:alt))

@@

```{r clean-data, warning=FALSE, message=FALSE}
data <- data_clean

write_csv(data, here("data", "final_data.csv"))
```

>>>>

col_names <- names(read_csv(here::here("data", "raw_data", "conjointqsf_final.csv")))
data <- read_csv(
  here::here("data", "conjointqsf_final.csv"),
  skip = 2,
  col_names = col_names
)
```

@@

```{r clean-data, warning=FALSE, message=FALSE}
design_orig <- read_csv(here("data", "derived_data", "design.csv")) %>% 
  rename(
    version = question_set,
    task = question,
    alt = choice
  ) %>% 
  gather(key = "atts", value = "levels", -c(version:alt))

@@

```{r clean-data, warning=FALSE, message=FALSE}
data <- data_clean %>% 
  select(-c("732d72a6-25a3-4194-8416-461acae30837.1.1_CBCONJOINT":"revision_CBCONJOINT"))

write_csv(data, here("data", "derived_data", "final_data.csv"))
```
